\section{The optimal solution}
As previously stated in the introduction we are trying to build a decentrilized version of Spotify.
This means that the system should be a music-streamer with an interface that runs in a browser,
and makes it possible for the users to search for a song.

All the users (peers) should be the ones to provide the content of the system.
We strove to achive a minimum implementation of spotify.
Spotify have a social aspect where you can login, save your playlist, see your friends activity and discover new music.
Spotify have ordered their music into genres and top charts.
In Spotify there is a radio function where music is played based on artist or genres.
A radio function would be a good function in our system, because it would make users want to discover new music.
Our system could have a navigation pane in the left side,
 where it could be possible to see what music your friends are listening to,
  browse the top 50 charts with mixed music and for a given genre.
Users could be given suggestions based on their recently played music.

\section{Planned System}
Given unlimited development time and resources; we would have build the above
mentioned system, however given the constraints of the project, we've been
forced to limit our scope, as such our planned system should:

Support music file sharing using WebTorrent,
searching for content in a DHT system,
and playback of music in the browser.
We plan the following features:
A radio function would be a good function in our system, because it would make users want to discover new music.
\begin{itemize}
	\item Users can add music to the network
	\item Users can search for content, artists and albums
	\item Users can get music from peers
	\item Users can see ongoing downloads
	\item Users can see seeding content
	\item Users can see local content
	\item Users can play local content
    \item Users can play downloading content (stream it)
    \item Users can set a storage / resource quota for the site
	\item Peers will automatically replicate bad health content
    \item Peers will utilize an intelligent eviction strategy, once their
        storage quota has been reached.
	\item Peers will use intelligent downloading strategy
	\item Peers persistantly store content
	\item Peers retrieve content from storage
	\item Peers seed local content
\end{itemize}

Searching for content should be handled by a Content Management System,
which should be a \acs{DHT} if one is available.
The \acs{GUI} has to be impressive enough to show that our system
could feasibly run behind a large, real-life, popular music service.

To sum up: Given the time constraints we have limited the scope of our system,
in particularely in the areas of the \acs{GUI}, and development of subprojects.
In case we cannot find a reliable, functioning \acs{DHT} system developed for WebRTC,
we will instead make use of a faked \acs{DHT}.

\section{Implemented System}
The following chapter sums up the implemented system, and Section~
\ref{sec:not-implemented} sums up the parts that we've not been able to implement.
